LDR: A 2nd-gen, National GeoLD System

### 2021-08-20 manuscript.tex
copyright notice

\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{listingsutf8}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}
\usepackage{footmisc}
\usepackage{bookmark}

@@

@@

\title{L4DR: A 2nd-gen, national GeoLD system}
\titlerunning{Loc-I for Disaster Recovery}

@@

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\linewidth]{images/l4dr-arch.png}
    \caption{An informal architecture diagram of the L4DR project's \textit{Linked Data} infrastructure}
    \label{fig:l4dr-arch}
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{listingsutf8}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}
\usepackage{footmisc}
\usepackage{bookmark}
\usepackage{tikz}

@@

\newcommand\copyrighttext{%
  \footnotesize Copyright ©2021 for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}
\newcommand\copyrightnotice{%
\begin{tikzpicture}[remember picture,overlay]
\node[anchor=south,yshift=10pt] at (current page.south) {\fbox{\parbox{\dimexpr\textwidth-\fboxsep-\fboxrule\relax}{\copyrighttext}}};
\end{tikzpicture}%
}

@@

\title{LDR: A 2nd-gen, National GeoLD System}
\titlerunning{Loc-I for Disaster Recovery}

@@

\copyrightnotice

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\linewidth]{images/l4dr-arch.png}
    \caption{An informal architecture diagram of the LDR project's \textit{Linked Data} infrastructure}
    \label{fig:l4dr-arch}
\end{figure}
